Effective Reionization Likelihood from Planck 2018 Data (?)

### 2020-12-03 paper/rei.tex
Before rearranging order of text to be PC results->KDE->model independent results.
Updates from Overleaf

$m_1$ & -0.119 & -0.098 & 1.000 & 0.657 & 0.208 & 0.094 & 0.067 \\ 
$m_2$ & -0.013 & 0.010 & 0.657 & 1.000 & -0.048 & 0.273 & 0.142 \\ 
$m_3$ & -0.115 & -0.065 & 0.208 & -0.048 & 1.000 & 0.064 & 0.018 \\ 
$m_4$ & -0.025 & 0.085  & 0.094 & 0.273 & 0.064 & 1.000 & 0.195 \\ 
$m_5$ & 0.118 & 0.072  & 0.067 & 0.142 & 0.018 & 0.195 & 1.000 \\

@@

We show a zoomed version of the $m_1-m_2$ plane in Fig.~\ref{fig:plot_m1m2_2015_vs_2018}, where we show beyond the physicality prior with the shaded area. [Discuss how the ellipse moved in the direction of lower tanh by going to lower m1.] 
In Fig.~\ref{fig:plot_m1m2_2015_vs_2018}, we also show using the PC chain covariance $\bf C$ (black dashed lines) what corresponds to an even simpler effective likelihood, which approximates the $m_a$ posterior as a multivariate Gaussian with mean $\bar{\bf m}$ and covariance $\bf C$ (also shown in Table~\ref{tab:PC_stats}:
\begin{equation}
 {\cal L}_{\rm gauss}\left({\rm data}|\mathbf{m} \right) = \frac{ e^{-\frac{1}{2} ({\bf m}-\bar{\bf m})^T {\bf C}^{-1} ({\bf m}-\bar{\bf m}) } }{\sqrt{(2\pi)^{N_{\rm PC}} | \mathbf{C}| }}.
 \label{eq:gaussian}
 \end{equation}
 This Gaussian approximation agrees well with the actual PC constraints, unlike in the Planck 2015 data where some differences were still visible on top of good agreement. The Gaussian likelihood is even faster than the kernel density estimate, and may be used to sample well-constrained models near the peak of the PC distributions, while becoming possibly less accurate near the tails of the distributions.

@@

\subsection{Implications for optical depth}

>>>>

$m_1$ & $-$0.116 & 0.030 & 1.000 & 0.657 & -0.208 & -0.094 & 0.067 \\
$m_2$ & $-$0.016 & 0.063 & 0.657 & 1.000 & 0.048 & -0.273 & 0.142 \\
$m_3$ & $$0.078 & 0.098 & -0.208 & 0.048 & 1.000 & 0.064 & -0.018 \\
$m_4$ & -0.077 & 0.131 & -0.094 & -0.273 & 0.064 & 1.000 & -0.195 \\
$m_5$ & 0.066 & 0.145 & 0.067 & 0.142 & -0.018 & -0.195 & 1.000 \\

@@

We show a zoomed version of the $m_1-m_2$ plane in Fig.~\ref{fig:plot_m1m2_2015_vs_2018}, where we show beyond the physicality prior with the shaded area. [Discuss how the ellipse moved in the direction of lower tanh by going to lower m1.] 
In Fig.~\ref{fig:plot_m1m2_2015_vs_2018}, we also show using the PC chain covariance $\bf C$ (black dashed lines) what corresponds to an even simpler effective likelihood, which approximates the $m_a$ posterior as a multivariate Gaussian with mean $\bar{\bf m}$ and covariance $\bf C$ (also shown in Table~\ref{tab:PC_stats}.

\begin{equation}
 {\cal L}_{\rm gauss}\left({\rm data}|\mathbf{m} \right) = \frac{ e^{-\frac{1}{2} ({\bf m}-\bar{\bf m})^T {\bf C}^{-1} ({\bf m}-\bar{\bf m}) } }{\sqrt{(2\pi)^{N_{\rm PC}} | \mathbf{C}| }}.
 \label{eq:gaussian}
 \end{equation}
 This Gaussian approximation agrees well with the actual PC constraints, unlike in the Planck 2015 data where some differences were still visible on top of good agreement. The Gaussian likelihood is even faster than the kernel density estimate, and may be used to sample well-constrained models near the peak of the PC distributions, while becoming possibly less accurate near the tails of the distributions.

@@

\section{Implications for optical depth}

\subsection{Cumulative optical depth}
